---
title: "ATbounds-vignette-RHC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ATbounds-vignette-RHC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ATbounds)
```

## Right Heart Catheterization Dataset 

In this vignette, we revisit the well-known Right Heart Catheterization Dataset available at [Vanderbilt Biostatistics Datasets Page](http://biostat.mc.vanderbilt.edu/wiki/Main/DataSets).
A cleaned version of the dataset is available in the package. 

```{r}
  Y <- RHC[,"survival"]
  D <- RHC[,"RHC"]
  X <- RHC[,-c(1,2)]
```

## Bounding the Average Treatment Effect 

We take the reference propensity score to be 
$\widehat{p}_{\text{RPS}}(X_i) = n^{-1} \sum_{i=1}^n D_i$
for each observation $i$. That is, we assign the sample proportion of the treated to the 
reference propensity scores uniformly for all observations. Of course, this is likely to be misspecified; however, it has the advantage that $1/\widehat{p}_{\text{RPS}}(X_i)$ is never close to 0 or 1.

```{r}
  rps <- rep(mean(D),length(D))  
```

We start with $Q=1$. 

```{r}
  atebounds(Y, D, X, rps, Q = 1)
```

We now consider $Q=2$ 

```{r}
  atebounds(Y, D, X, rps, Q = 2)
```

and $Q=3$. 

```{r}
  atebounds(Y, D, X, rps, Q = 3)
```

Finally, we take a relatively large $Q = 10$.

```{r}
  atebounds(Y, D, X, rps, Q = 10)
```


## Bounding the Average Treatment Effect on the Treated

We now look at ATT with a few values of $Q$.

```{r}
  attbounds(Y, D, X, rps, Q = 3)
  attbounds(Y, D, X, rps, Q = 5)
  attbounds(Y, D, X, rps, Q = 10)
  
```


